\begin{titlepage}
    \thispagestyle{empty} % Remove page numbers
    \setstretch{1.5} % Line spacing, make sure the setspace package is included in document.tex

    \begin{center}
        \textbf{\Large ABSTRACT}
    \end{center}

    \vspace{1cm} % Vertical space

    \noindent CAGIDE FIALHO, G. Project Report on Numerical Methods for Differential Equations II. 2024. 25 p. Course Completion Work for Numerical Methods for Differential Equations II (Bachelor’s in Computer Engineering) – Bachelor’s in Computer Engineering, State University of Rio de Janeiro, Nova Friburgo, 2024.

    \vspace{0.4cm} % Vertical space

    This work investigates numerical and analytical solutions to advection and advection-diffusion equations, utilizing Lagrangian methods and Variable Separation. The study focuses on the influence of advection and diffusion coefficients in an infinite domain, exploring how velocity and diffusion coefficient affect the dispersion and transport of solutes. Through detailed numerical simulations, the characteristics of the solutions under various conditions were examined, providing insights into the dynamics of solute in unidimensional flows. Comparative analyses between pure advection and advection-diffusion solutions highlight the significant role of diffusion in modifying the concentration profile, particularly at higher coefficients. This study not only reinforces the theoretical understanding of differential equations in modeling physical phenomena but also serves as a practical reference for engineers and scientists to apply in engineering and environmental contexts.

    \vspace{0.4cm} % Vertical space

    \textbf{Keywords}: Numerical Methods, Advection Equations, Advection-Diffusion, d’Alembert Solution, Variable Separation, Numerical Simulation.
\end{titlepage}
