\begin{titlepage}
    \thispagestyle{empty} % Remove page numbers
    \setstretch{1.5} % Line spacing, make sure the setspace package is included in document.tex

    \begin{center}
        \textbf{\Large ABSTRACT}
    \end{center}

    \vspace{1cm} % Vertical space

    \noindent CAGIDE FIALHO, G. Project Report on Numerical Methods for Differential Equations II. 2024. 16 p. Course Completion Work for Numerical Methods for Differential Equations II (Bachelor’s in Computer Engineering) – Bachelor’s in Computer Engineering, State University of Rio de Janeiro, Nova Friburgo, 2024.

    \vspace{0.4cm} % Vertical space

    This work analyzes numerical and analytical solutions to advection and advection-diffusion equations in an domain, considering the influence of velocity and diffusion coefficients on the transport and dispersion of substances. Analytical solutions were obtained using characteristic methods and variable transformations, while numerical solutions were developed using methods such as Upwind, Lax-Wendroff, Beam-Warming, and Fromm. The results of numerical simulations highlight the differences between pure advection and advection-diffusion models, demonstrating how diffusion contributes to a more homogeneous concentration over time. The comparative analysis of the solutions reveals the importance of the diffusion coefficient in influencing solute dispersion, serving as a tool for modeling natural phenomena and providing practical applications in engineering and environmental sciences.

    \vspace{0.4cm} % Vertical space

    \textbf{Keywords}: Numerical Methods, Advection Equation, Advection-Diffusion Equation, Characteristics, Numerical Simulation, Solute Dispersion.
\end{titlepage}
